Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for S\&R Usage

### 2022-09-01 paper/paper.tex
UAV and robor ok, fa=sin(), fs=square wavw, problem of scale of system solved: UAV ~= 10*robot. add smoothModel.set_real_signal(), simplified code.

Now, substituting (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(r(t))\ddot{x}(t)$ from the left and right sides, we have:

@@

        & (M(x(t))-M(r(t)))\ddot{x}(t) + H(x(t),\dot{x}(t)) \\
        & =(M(r(t))(\ddot{r}(t)-\ddot{x}(t)) + M(r(t))u_{fb}(t) \\

@@

By Multipling $M(r(t))^{-1}$ from the left and right sides and with some arrangments, we have:

@@

where $f_1(t) = M(r(t))^{-1}(-\Delta M -\Delta H + d_1(t))\in\mathbb{R}^n$ is the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.

>>>>

Now, substituting (\ref{eq:control}) into (\ref{eq:agent d1}) and subtracting $M(x(t))\ddot{r}(t)$ from the left and right sides, we have:

@@

        & M(x(t))(\ddot{x}(t)-\ddot{r}(t)) + H(x(t),\dot{x}(t)) \\
        & =(M(r(t))-M(x(t)))\ddot{r}(t) + M(r(t))u_{fb}(t) \\

@@

By Multipling $M(x(t))^{-1}$ from the left and right sides and with some arrangments, we have:

@@

where $f_1(t) = M(x(t))^{-1}(-\Delta M (\ddot{r}(t)+u_{fb}(t)) -\Delta H + d_1(t))\in\mathbb{R}^n$ is the actuator fault signal, $\Delta M \triangleq M(x(t)) - M(r(t)), \Delta H \triangleq H(x(t),\dot{x}(t)) - H(r(t),\dot{r}(t))$ are the error terms from feedforward compensation, and $e(t)= x(t)-r(t)$ is the tracking error.
